---
title: "Using my_lm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using my_lm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The `my_lm_package` is a custom implementation of the base R `lm` function. It provides additional flexibility and diagnostics for fitting linear models, including support for weighted least squares, offsets, and handling singular fits.

In this vignette, we demonstrate the basic usage of `my_lm`, compare its output with base R's `lm`, and evaluate its performance.

------------------------------------------------------------------------

# Fitting a Basic Model

To fit a linear model using `my_lm`, simply specify the formula and the data:

```{r}
library(homework3)

# Load the mtcars dataset
data(mtcars)

# Fit a model with mpg as the response and wt and cyl as predictors
fit <- my_lm(mpg ~ wt + cyl, data = mtcars)

# Display the summary of the model
summary(fit)
```

------------------------------------------------------------------------

# Comparing `my_lm` with Base R's `lm`

The `my_lm` function is designed to mimic the behavior of base R's `lm`. Let's compare the two using the same dataset and model:

```{r}
# Fit a model using base R's lm
fit_base <- lm(mpg ~ wt + cyl, data = mtcars)

# Compare coefficients
all.equal(fit$coefficients, coef(fit_base))

# Compare fitted values
all.equal(fit$fitted.values, fitted(fit_base))

# Compare residuals
all.equal(fit$residuals, residuals(fit_base))
```

------------------------------------------------------------------------

# Handling Weights and Offsets

The `my_lm` function allows you to specify weights and offsets to adjust the regression fit.

### Using Weights

Weighted least squares fitting can be performed by providing a `weights` vector:

```{r}
# Define weights (example: all equal weights)
weights <- rep(1, nrow(mtcars))

# Fit the model with weights
fit_weighted <- my_lm(mpg ~ wt + cyl, data = mtcars, weights = weights)

# Display summary
summary(fit_weighted)
```

### Using Offsets

Offsets can be added to account for known components in the linear predictor:

```{r}
# Define offsets
offset <- rep(2, nrow(mtcars))

# Fit the model with offsets
fit_offset <- my_lm(mpg ~ wt + cyl, data = mtcars, offset = offset)

# Display summary
summary(fit_offset)
```

------------------------------------------------------------------------

# Diagnosing Singular Fits

The `my_lm` function provides diagnostics for singular fits and can handle them gracefully.

```{r}
# Create data with perfect collinearity
singular_data <- data.frame(
  y = c(1, 2, 3),
  x1 = c(1, 1, 1),
  x2 = c(2, 2, 2)
)

# Attempt to fit the model
try(fit_singular <- my_lm(y ~ x1 + x2, data = singular_data, singular.ok = FALSE))
```

By setting `singular.ok = TRUE`, you can proceed with a warning instead of an error.

------------------------------------------------------------------------

# Performance Benchmarking

We benchmark `my_lm` against base R's `lm` to compare their efficiency:

```{r}
library(bench)
library(testthat)

# Simulated dataset
set.seed(123)
n <- 1000
x1 <- rnorm(n)
x2 <- rnorm(n)
y <- 3 + 2 * x1 - 1.5 * x2 + rnorm(n)

simulated_data <- data.frame(y = y, x1 = x1, x2 = x2)

# Fit models using both my_lm and base lm
fit_my_lm <- my_lm(y ~ x1 + x2, data = simulated_data)
fit_base_lm <- lm(y ~ x1 + x2, data = simulated_data)

# Correctness: Compare coefficients, fitted values, and residuals
cat("\nCorrectness Check\n")
all.equal(fit_my_lm$coefficients, coef(fit_base_lm), tolerance = 1e-6)
all.equal(fit_my_lm$fitted.values, fitted(fit_base_lm), tolerance = 1e-6)
all.equal(fit_my_lm$residuals, residuals(fit_base_lm), tolerance = 1e-6)

# Efficiency: Benchmark my_lm vs lm
cat("\nEfficiency Benchmark\n")
library(bench)

# Benchmarking Coefficients Only
cat("\nEfficiency Benchmark\n")
benchmark_results <- bench::mark(
  my_lm = {
    fit <- my_lm(mpg ~ wt + hp + cyl, data = mtcars)
    as.numeric(fit$coefficients)  # Ensure coefficients are a numeric vector
  },
  base_lm = {
    fit <- lm(mpg ~ wt + hp + cyl, data = mtcars)
    as.numeric(coef(fit))  # Ensure coefficients are a numeric vector
  }
)

print(benchmark_results)
# Correctness Check for Coefficients
fit_my <- my_lm(mpg ~ wt + hp + cyl, data = mtcars)
fit_base <- lm(mpg ~ wt + hp + cyl, data = mtcars)

cat("\nCoefficient Comparison\n")
print(all.equal(as.numeric(fit_my$coefficients), as.numeric(coef(fit_base)), tolerance = 1e-6))


```

The results indicate that `my_lm` performs comparably to base R's `lm`, with minor overhead due to additional diagnostics.

------------------------------------------------------------------------

# Conclusion

The `my_lm` function provides a robust alternative to base R's `lm`. With support for weighted least squares, offsets, and singular fit diagnostics, it is well-suited for a variety of linear regression tasks.

